\ldots

### 2016-02-19 figures/best.tex
Lexical tasks
Figures

\begin{figure*}
  \centering
  \begin{subfigure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/SimLex999-ppmi-best.pdf}
    \caption{SimLex-999}
    \label{fig:simlex-ppmi-best-simlex}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/men-ppmi-best.pdf}
    \caption{MEN}
    \label{fig:simlex-ppmi-best-men}
  \end{subfigure}

  \caption{\textbf{SPMI best configurations.} Black line shows the best results reported by \protect\newcite{TACL570}.}
  \label{fig:simlex-ppmi-best}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \begin{subfigure}[b]{\textwidth}
    \centerline{\includegraphics[width=1.1\textwidth]{supplement/figures/SimLex999-best}}
    \caption{\textbf{SimLex-999.} The black line refers to the score of 0.393.
      This work: 0.385,
      SGNS: 0.438,
      GloVe: 0.398.
    }
    \label{fig:simlex-ppmi-best-simlex}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \centerline{\includegraphics[width=1.1\textwidth]{supplement/figures/men-best}}
    \caption{\textbf{MEN.} The black line refers to the score of 0.745.
      This work: 0.765,
      SGNS: 0.774,
      GloVe: 0.729.
    }
    \label{fig:simlex-ppmi-best-men}
  \end{subfigure}

  \caption{\textbf{SPMI best configurations.} Black line shows the best count models reported by \protect\newcite{TACL570}. We also give our best score, SGNS and GloVe numbers from that study for comparison.}
  \label{fig:simlex-ppmi-best}
\end{figure*}

### 2016-02-19 paper.tex
Figures

\def\relevant/{Relevant@3}
\def\topRR/{Top Reciprocal Rank}
\def\RR/{Reciprocal Rank}

@@

% Vector space models of language were inspired by the idea of \newcite{harris1954distributional} and \newcite{firth1957lingtheory} that meanings of words can be deduced from their co-occurrence with other words in natural text. If a word co-occurs with a context word more often than can be expected, this context word is indicative of the word's meaning, while the opposite indicates disjointness in meaning.
% \newcite{Dagan:1993:CWS:981574.981596} were among the first to apply this idea computationally and to represent word meaning by an ordered range of values of
% \emph{mutual information}\footnote{Also known as pairwise or pointwise mutual information and commonly abbreviated as PMI.} \cite{church1990word}.
% Each value expresses the ratio between the observed and the expected co-occurrence, and, therefore, measures the association of the target word with a reference word. A word could thus be expressed as a vector with a set of contextual terms as its features, and as their weights a measure of association. This idea forms the basis of distributional semantics and has become mainstream in information retrieval and natural language processing tasks.

% Over the last decades, various information-theoretic alternatives and refinements to mutual information have been introduced to capture lexical semantics. The most notable are \emph{positive PMI} (PosPMI, \newcite{BullinariaLevy07}) and \emph{local mutual information} (LMI, \newcite{evert2008corpora}).
% These measures differ from PMI in their treatment of frequencies below expectation, and in the weight assigned to observed frequencies, embodied in additional multiplication factors.

\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, most notably \emph{shifted PMI} abbreviated as \texttt{neg} and \emph{context distribution smoothing} referred to as \texttt{cds}. Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces with word vector  dimensionality of almost \textbf{200K}. As such, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC}.

@@

PMI is not directly applicable to the co-occurrence matrix because non-observed co-occurrences lead to infinite PMI values which in turn make it impossible to compute similarity. A straightforward ``fix'' to this problem is to replace all infinities with zeroes. Such a replacement preserve sparsity of the input co-occurrence matrix. Later in the paper, we use PMI to refer to a weighting with this fix.

@@

10K dimensional \SPMI/ is, indeed, the least sensitive to parameter selection. For models with dimensionality greater than 20K, context distribution smoothing should be used with $\alpha = 0.75$. For models with dimensionality lower than 20K, it is beneficial to use global context probabilities. Shifting also depends on the dimensionality, models with up to 20K dimensions should set $k = 0.7$ and models with a higher number of dimensions should set $k = 5$. Note, however, that there might be a finer grained $k$ tuning which we avoid in order to avoid overfitting.

\logNSPMI/ should be used with global context probabilities for models with vector dimensions up to 20K. For more dimensional spaces, smoothing should be applied with $\alpha = 0.75$, which is similar to \SPMI/. Shifting should be applied with $\alpha = 1.4$ for models with less than 20K dimensions and $\alpha = 5$ for models with more than 20K dimensions. In contrast to \SPMI/, which might require change of $k$ as the dimensionality increases, $\alpha = 1.4$ is a much robust choice for \logNSPMI/.

@@

\NSCPMI/ with dimensions less than 20K global context probability should be used and $k = 1.4$. Otherwise local context probability without smoothing and $k = 5$ is suggested.

@@

Heuristics for \logNCPMI/ and \CPMI/ follow the best selection, but with a wider gap than the PPMI models. In general $n$ weighted models do not perform as good as others.

Finally, to see whether the heuristics are applicable to other datasets, we contrast the selected models with the best scores on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}). Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection.

>>>>

@@

\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, most notably shifting and context distribution smoothing. Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces with word vector  dimensionality of almost \textbf{200K}. As such, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC}.

@@

PMI is not directly applicable to the co-occurrence matrix because non-observed co-occurrences lead to infinite PMI values which in turn make it impossible to compute similarity. A straightforward ``fix'' to this problem is to replace all infinities with zeroes. Later in the paper, we use PMI to refer to a weighting with this fix.

@@

10K dimensional \SPMI/ is the least sensitive to parameter selection. For models with dimensionality greater than 20K, context distribution smoothing should be used with $\alpha = 0.75$. For models with dimensionality lower than 20K, it is beneficial to use global context probabilities. Shifting also depends on the dimensionality, models with up to 20K dimensions should set $k = 0.7$ and models with a higher number of dimensions should set $k = 5$. Note, however, that there might be a finer grained $k$ selection criteria, which we do not report in order to avoid overfitting.

\logNSPMI/ should be used with global context probabilities for models with vector dimensions up to 20K. For more dimensional spaces, smoothing should be applied with $\alpha = 0.75$, which is similar to \SPMI/. Shifting should be applied with $k = 0.5$ for models with less than 20K dimensions and $k = 1.4$ for models with more than 20K dimensions. In contrast to \SPMI/, which might require change of $k$ as the dimensionality increases, $k = 1.4$ is a much robust choice for \logNSPMI/.

@@

\NSCPMI/ with dimensions less than 20K should using with global context probability and $k = 1.4$. Otherwise, local context probability without smoothing and $k = 5$ is suggested.

@@

Heuristics for \logNCPMI/ and \CPMI/ follow the best selection, but with a wider gap than the SPMI models. In general $n$ weighted models do not perform as good as others.

Finally, to see whether the heuristics are applicable to other datasets, we contrast the selected models with the best scores on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}). Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection for SPMI and SCPMI.
